---
title: "Combined RNAi screen"
author: "Nathaniel Evans"
date: "October 4, 2019"
output:
  html_document: 
    theme: flatly 
    highlight: kate
    toc: true
    toc_depth: 2
    toc_float : true
    smooth_scroll: true
    number_sections : false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)
```


# overview 






# data in 

[info]
[Combined RNAi - source](https://ndownloader.figshare.com/files/13515395)

### Citation 

James M. McFarland, Zandra V. Ho, Guillaume Kugener, Joshua M. Dempster, Phillip G. Montgomery, Jordan G. Bryan, John M. Krill-Burger, Thomas M. Green, Francisca Vazquez, Jesse S. Boehm, Todd R. Golub, William C. Hahn, David E. Root, Aviad Tsherniak. (2018). Improved estimation of cancer dependencies from large-scale RNAi screens using model-based normalization and data integration. Nature Communications 9, 1. https://doi.org/10.1038/s41467-018-06916-5 


```{r}
rnai.dat <- as.data.frame(fread('./../data/D2_combined_gene_dep_scores.csv', sep=','))
rnai.dat <- rnai.dat %>% pivot_longer(-V1, names_to='cell_line') %>% mutate(gene = V1, effect = value) %>% select(-V1, -value)

rnai.dat %>% head()
```






```{r}
CCLE.rnaSeq <- as.data.frame(fread('./../data/CCLE_RNAseq_rsem_genes_tpm_20180929.txt', sep='\t'))

CCLE.rnaSeq[1:5, 1:5]

```